---
title: "Using complete.design for Experimental Design"
author: "Wang Xianjue"
date: "2024-12-08"
output: rmarkdown::html_vignette
vignette: >
  %\\VignetteIndexEntry{Using complete.design for Experimental Design}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

# Introduction

The `complete.design` function is an R utility designed for creating full factorial experimental designs. This vignette explains the function's purpose, parameters, and provides examples to illustrate its usage.

## Function Overview

### Description
The `complete.design` function generates a complete factorial design based on the specified factors and their levels. It allows flexibility in defining factors as integers, character vectors, or complex data frames.

### Key Features
- Support for integer-based levels, character-based levels, and data frames as factors.
- Ability to include experiment numbering.
- Allows repetition of each combination via the `size` parameter.

---

## Function Usage
complete.design(varlist, numbering = TRUE, size = 1)

### Parameters
- `varlist`: A list where each element represents a factor. It can be:
  - A positive integer: Defines the number of levels for a factor.
  - A vector: Specifies the exact levels for a factor.
  - A data frame: Represents a complex factor with multiple columns.
- `numbering`: Logical, whether to include an experiment number column (`TRUE` by default).
- `size`: Integer, specifies the number of repetitions for each experimental combination (default = 1).

### Returns

A data frame containing all possible combinations of the specified factors, with optional numbering and repetitions.

---

## Examples

### Example 1: Simple Factorial Design

Create a design with three factors:
- Factor `f1` with 3 levels.
- Factor `f2` with two character levels: `a` and `b`.
- Factor `f3` with 4 levels.

```{r}
design <- complete.design(list(f1 = 3, f2 = c("a", "b"), f3 = 4))
head(design)
```
###Example 2: Repeated Combinations
Repeat each combination twice:
```{r}
design <- complete.design(list(f1 = 3, f2 = c("a", "b"), f3 = 4), size = 2)
head(design)
```
###Example 3: Complex Factor with Data Frame
Create a factorial design where one factor (f3) is a data frame:
```{r}
design <- complete.design(list(
  f1 = 3,
  f2 = c("a", "b"),
  f3 = data.frame(
    fa = c(0.01, 0.05, 0.1),
    fb = c("x", "x", "y")
  )
), size = 2)
head(design)
```
###Error Handling
The function automatically validates inputs. For example, providing invalid levels results in an error:
```{r error=TRUE}
complete.design(list(f1 = c(1, 1, 2)))
```

