---
title: "Using complete.design for Experimental Design"
author: "wang xianjue"
date: "`2024.12.1`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using complete.design for Experimental Design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The `complete.design` function is an R utility designed for creating full factorial experimental designs. This vignette explains the function's purpose, parameters, and provides examples to illustrate its usage.

## Function Overview

### Description
The `complete.design` function generates a complete factorial design based on the specified factors and their levels. It allows flexibility in defining factors as integers, character vectors, or complex data frames.

### Key Features
- Support for integer-based levels, character-based levels, and data frames as factors.
- Ability to include experiment numbering.
- Allows repetition of each combination via the `size` parameter.

---

## Function Usage
complete.design(varlist, numbering = TRUE, size = 1)

Parameters

	•	varlist: A list where each element represents a factor. It can be:
	•	A positive integer: Defines the number of levels for a factor.
	•	A vector: Specifies the exact levels for a factor.
	•	A data frame: Represents a complex factor with multiple columns.
	•	numbering: Logical, whether to include an experiment number column (TRUE by default).
	•	size: Integer, specifies the number of repetitions for each experimental combination (default = 1).

Returns

A data frame containing all possible combinations of the specified factors, with optional numbering and repetitions.

Examples

Example 1: Simple Factorial Design

Create a design with three factors:
	•	Factor f1 with 3 levels.
	•	Factor f2 with two character levels: a and b.
	•	Factor f3 with 4 levels.

```{r}
design <- complete.design(list(f1 = 3, f2 = c("a", "b"), f3 = 4))
head(design)
```
Example 2: Repeated Combinations

Repeat each combination twice:

```{r}
design <- complete.design(list(f1 = 3, f2 = c("a", "b"), f3 = 4), size = 2)
head(design)
```
Example 3: Complex Factor with Data Frame

Create a factorial design where one factor (f3) is a data frame:
```{r}
design <- complete.design(list(
  f1 = 3,
  f2 = c("a", "b"),
  f3 = data.frame(
    fa = c(0.01, 0.05, 0.1),
    fb = c("x", "x", "y")
  )
), size = 2)
head(design)
```
Error Handling

Invalid Input

If invalid inputs are provided (e.g., a factor with non-unique levels or negative integers), the function will stop with an error:
complete.design(list(f1 = c(1, 1, 2)))
# Error: 非法输入！

Additional Notes

	•	The function supports complex experimental designs with multiple factors, including nested and multicolumn factors.
	•	It automatically handles invalid inputs, ensuring robustness.

Suggested Packages

This function works well with the following packages:
	•	knitr and rmarkdown: For generating reproducible reports.
	•	tidyverse: For downstream data manipulation and visualization.

Conclusion

The complete.design function provides a flexible and powerful tool for generating experimental designs in R. Its support for various factor types and options for repetitions makes it highly versatile for both simple and complex experiments.

```